### 2024-11-16 conteudo/preliminar/results.tex
remove TODO's
redo patch info

The refactoring of the second function pair, however, was successful. We submitted this refactoring as a patch to the AMD Display driver to obtain feedback from the maintainers.
\todo[inline]{Atualizar ... tentar colocar algo do feedback que recebeu da revisão do patch}

\input{conteudo/preliminar/cronograma}
\todo[inline]{Atualizar o cronograma, alocando tempo para evolucao da ferramenta (DONE?) }

@@

\todo[inline]{colocar aqui também algo da evolucao da ferramenta que sera feito até o final do mestrado (DONE?) }

>>>>

The refactoring of the second function pair, however, was successful. 
We submitted this refactoring as a patch to the AMD Display driver to obtain feedback 
from the maintainers.

The process of sending the patch was more time consuming then the expected . We 
initially submitted the patch on August 9th, 2024, but did not receive any 
replies. As a result, we had to resend it on October 9th, 2024, and finally 
received an initial response on 
November 3rd, 2024. 
While talking to our point of contact for the AMD Display driver, we discovered 
new information about the driver's processes. Some of the code in the driver is 
shared across all operating systems that support the implemented GPUs. This creates 
a challenging process within AMD to format and submit changes across the supported 
systems while simultaneously applying measures to mitigate errors.
Additionally, we discovered that duplicated code isn’t seen as negatively by AMD 
display driver developers as it is in the literature. One example shared with us 
is that duplicated code makes GPU driver code more independent, letting developers 
make changes to a GPU without worrying about testing compatibility with other GPUs, 
which helps save a lot of time and effort.

Regarding the patch content, only minor changes were requested to align with code 
style and best practices that were initially unknown to us. More details of the 
patch can be found in Appendix \ref{app:feedback}.

\input{conteudo/preliminar/cronograma}

@@
